---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EIAapi

<!-- badges: start -->
<!-- badges: end -->
WIP - pre-spell check

The EIAapi package provides function to query data from the [EIA API v2](https://www.eia.gov/opendata/). 

## Requirments

To pull data from the API using this package you will need:

- jq - The package uses on the back-end [jq](https://stedolan.github.io/jq/) to parse 
the API output from JSON to tabular format. To download and install jq follow the instructions on the [download page](https://stedolan.github.io/jq/download/).
- API key - To query the EIA API, you will need to register to the service to receive API key.

## Installation

Currently, the package is under development and not available on CRAN. You can 
install the experiment version from Github:

``` r
# install.packages("devtools")
devtools::install_github("RamiKrispin/tsafr/R/EIAapi")
```

## Query data 

The following example demonstrate

```{r}
# Pulling the API key from my renviron file
key <- Sys.getenv("eia_key")

```


